Streaming Fact Extraction for Wikipedia Entities at Web-Scale

### 2013-11-18 paper/flairs27/content/results.tex
Ready for submission

\begin{tabular}{|l|l|c|}
\hline 
\textbf{Document Type} & \textbf{\# of Documents} &  \textbf{Slots Found}\\ 
\hline 
Arxiv & 10988 & \\ \hline
 Classified & 34887 & \\ \hline
 Forum & 77674 & \\ \hline
 Linking & 12947 & \\ \hline
 Mainstream News & 141936 & \\ \hline
 Memetracker & 4137 & \\ \hline
 News & 280629 & \\ \hline
 Review & 6347 & \\ \hline
 Social & 688848 & \\ \hline
 Weblog & 740987 & \\ \hline
\hline 
\end{tabular} 
\end{table}

@@

\begin{table}
\caption{Recall Measure: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|p{13mm}|p{22mm}|}
\hline 
 \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity \hspace{5 mm} Coverage} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

>>>>

\begin{tabular}{|p{3.8cm}|p{3cm}|}
\hline 
\textbf{Document Type} & \textbf{\# of Documents}\\ 
\hline 
Arxiv & 10988  \\ \hline
 Classified & 34887  \\ \hline
 Forum & 77674  \\ \hline
 Linking & 12947  \\ \hline
 Mainstream News & 141936  \\ \hline
 Memetracker & 4137  \\ \hline
 News & 280629  \\ \hline
 Review & 6347 \\ \hline
 Social & 688848 \\ \hline
 Weblog & 740987  \\ \hline
\hline 
\end{tabular} 
\end{table}

@@

\begin{table}[t]
\caption{Recall Measure: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath}
\centering
\label{table:finalresultrecall}
\begin{tabular}{|l|p{13mm}|p{22mm}|}
\hline 
 \textbf{Slot Name} & \textbf{Instances Found} & \textbf{Entity \hspace{5 mm} Coverage} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline
